\documentclass[11pt,openright,twoside,a4paper]{report}
%%
%% This document template assumes you will use pdflatex.  If you are using
%% latex and dvipdfm to translate to pdf, insert dvipdfm into the options.
%%

\include{DissertationDefinitions}    %% These are the includes required for the doc


\title{Content-based Video Retrieval for Pattern Matching Video Clips}
\author{Adam Jaamour}
\date{Bachelor of Science in Computer Science with Honours\\The University of Bath\\May 2019}

\apptocmd{\thebibliography}{\csname phantomsection\endcsname\addcontentsline{toc}{chapter}{\bibname}}{}{}


\begin{document}


% Set this to the language you want to use in your code listings (if any)
\lstset{language=Python,breaklines,breakatwhitespace,basicstyle=\small}


\setcounter{page}{0}
\pagenumbering{roman}


\maketitle
\newpage


% Set this to the number of years consultation prohibition, or 0 if no limit
\consultation{0}
\newpage


\declaration{Content-based Video Retrieval for Pattern Matching Video Clips}{Adam Jaamour}
\newpage


\abstract
Your abstract should appear here.  An abstract is a short
paragraph describing the aims of the project, what was
achieved and what contributions it has made.
\newpage


\tableofcontents
\newpage
\listoffigures
\newpage
\listoftables
\newpage


\chapter*{Acknowledgements}
Add any acknowledgements here.
\newpage


\setcounter{page}{1}
\pagenumbering{arabic}



\chapter{Introduction}
%% Uncomment this to include a separate tex file wih the introduction contents
%\include{introduction.tex}

This is the introductory chapter.

Citation examples

citation example \cite{2012-Patel-Meshram}

citation example \cite{2000-Petkovic}

citation example \cite{2015-Kalenzaga}

citation example \cite{2008-Bradski-Kaehler}

\section{Example Section}
Like all chapters, it will have a number of sections

\subsection{Example Subsection}
\ldots and sub-sections

\subsubsection{Example sub-subsection}
\ldots and sub-subsections.

\begin{table}[htb]
\begin{center}
\caption{An example table}
\label{Example-Table}
\begin{tabular}{|l|l|}
\hline
Items & Values \\
\hline
\hline
Item 1 & Value 1 \\
Item 2 & Value 2 \\
\hline
\end{tabular}
\end{center}
\end{table}

\section[short section title]{Another section}
Another section, just for good measure.
You can reference a table, figure or equation using \verb|\ref|, just
like this reference to table \ref{Example-Table}.

\section{Example lists}

\subsection{Enumerated}

\begin{enumerate}
\item Example enumerated list
  \begin{itemize}
  \item a nested enumerated list item
  \end{itemize}
\item Second item in the list
\end{enumerate}

\subsection{Itemized}

\begin{itemize}
\item Example itemized list
  \begin{itemize}
  \item a nested itemized list item
  \end{itemize}
\item Second item in the list
\end{itemize}

\subsection{Description}

\begin{description}
\item[Item 1] Example description list
\item[Item 2] Second item in the list
\end{description}


\chapter{Literature Survey}
%% Uncomment this to include a separate tex file wih the introduction contents
%\include{litsurvey.tex}
This is the chapter for your Literature Survey.

You will wish to cite authors like \cite{latex} or \cite{btxdoc}.  Alternate
commands are used to cite \citeasnoun{latex} as a noun, or cite
\possessivecite{latex} work possessively, or add text to the citation,
\citeaffixed{latex}{e.g.}.

If these citations do not compile correctly, ensure you have the Harvard
package installed.  You can pick up the Harvard package in the zip file
of the dissertation template files you downloaded.


%%
%% NOTE: Replace the following with chapters that are appropriate for your
%%       style of project.  It is unlikely these will fit your project perfectly.
%%

\chapter{Requirements}
If you are doing a primarily software development project, this is the
chapter in which you review the requirements decisions and
critique the requirements process.


\chapter{Design}
This is the chapter in which you review your design decisions at various
levels and critique the design process.


\chapter{Implementation and Testing}
This is the chapter in which you review the implementation and testing
decisions and issues, and critique these processes.

Code can be output inline using \verb@\lstinline|some code|@.  For example,
this code is inline: \lstinline|public static int example = 0;|  (I have
used the character \verb@|@ as a delimiter, but any non-reserved character
not in the code text can be used.)

Code snippets can be output using the \verb|\begin{lstlisting} ... \end{lstlisting}|
environment with the code given in the environment.  For
example, consider listing \ref{Example-Code}, below.

\begin{lstlisting}[breaklines,breakatwhitespace,caption={Example code},label=Example-Code]
public static void main() {

  System.out.println("Hello World");

}
\end{lstlisting}

Code listings are produced using the package ``Listings''.  This has many
useful options, so have a look at the package documentation for further
ideas.


\chapter{Results}
This is the chapter in which you review the outcomes, and
critique the outcomes process.  You may include user evaluation here
too.


%%
%% Now we are back to the standard project contents that you should include
%%

\chapter{Conclusions}
%% Uncomment this to include a separate tex file wih the conclusion contents
%\include{conclusion.tex}

This is the chapter in which you review the major achievements in the
light of your original objectives, critique the process, critique your
own learning and identify possible future work.


\bibliography{Bibliography}


\appendix

%%
%% Use the appendix for major chunks of detailed work, such as these. Tailor
%% these to your own requirements
%%

\chapter{Design Diagrams}

\chapter{User Documentation}

\chapter{Raw results output}

\chapter{Code}

%%
%% NOTE that for this to typeset correctly, ensure you use the pdflatex
%%      command in preference to the latex command.  If you do not have
%%      the pdflatex command, you will need to remExample-TableExample-Tableove the landscape and
%%      multicols tags and just make do with single column listing output
%%

\begin{landscape}
\begin{multicols}{2}
\section{File: main.py}
\lstinputlisting[basicstyle=\scriptsize]{main.py}
\end{multicols}
\end{landscape}

\end{document}
