This appendix includes the main code sections of the system in a lightweight form, with omitted comments and condensed formats. The code is organised by module.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% MAIN %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Main Module}

The \textit{main.py} module contains the program entry point that parses the command line argument in order to decide which phase to execute. Contains the three functions to begin each phase, include the off-line colour-based feature extraction, the on-line retrieval and database pre-processing phases.

\subsection{Argument Parsing}
\label{sec:code-listings-argument-parsing}

The program entry point. Parses command line input to decide which phase of the system to run.

\lstinputlisting{code-listings/main/argument_parsing.py}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Initial Off-line Colour-based Feature Extraction Phase Function}
\label{sec:code-off_line_colour_based_feature_extraction_phase}

Generates and stores averaged greyscale, RGB and HSV histograms for all the videos in the directory-based database.

\lstinputlisting{code-listings/main/off_line_colour_based_feature_extraction_phase.py}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Initial On-line Retrieval Phase Function}
\label{sec:code-on_line_retrieval_phase}

Prompts the user to stabilise and crop the query video before generating the same averaged greyscale, RGB and HSV histograms to compare with the database videos' previously stored histograms using distance metrics.

\lstinputlisting{code-listings/main/on_line_retrieval_phase.py}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Initial Database Pre-Processing Phase}
\label{sec:code-database_preprocessing_phase}

Applies a shot boundary detection algorithm to a video for segmentation.

\lstinputlisting{code-listings/main/database_preprocessing_phase.py}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% HISTOGRAMS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\section{Histograms Module}

The \textit{histogram.py} module contains the HistogramGenerator class with functions to generate, average, store and compare greyscale, RGB and HSV histograms.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{High Level Module Overview}
\label{sec:code-high-level-module-overview}

A high-level overview of the module's classes and functions.

\lstinputlisting{code-listings/histogram/histogram_module_high_level.py}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Single Greyscale Histogram Generation}
\label{sec:code-single_grey_histogram_generation}

Generates multiple greyscale histograms (one every second) for a video.

\lstinputlisting{code-listings/histogram/single_grey_histogram_generation.py}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Single RGB Histogram Generation}
\label{sec:code-single_rgb_histogram_generation}

Generates multiple RGB histograms (one every second) for a video.

\lstinputlisting{code-listings/histogram/single_rgb_histogram_generation.py}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Single HSV Histogram Generation}
\label{sec:code-average_and}

Generates multiple HSV histograms (one every second) for a video.

\lstinputlisting{code-listings/histogram/single_hsv_histogram_generation.py}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Average \& Store Greyscale Histogram}
\label{sec:code-generate_and_store_average_grey_histogram}

Generates a single greyscale histogram by averaging all histograms of a video before normalising it and saving the results to a plain text file.

\lstinputlisting{code-listings/histogram/generate_and_store_average_grey_histogram.py}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Average \& Store RGB Histogram}
\label{sec:code-generate_and_store_average_rgb_histogram}

Generates a single RGB histogram by averaging all histograms of a video before normalising it and saving the results to a plain text file.

\lstinputlisting{code-listings/histogram/generate_and_store_average_rgb_histogram.py}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Average \& Store HSV Histogram}
\label{sec:code-generate_and_store_average_hsv_histogram}

Generates a single HSV histogram by averaging all histograms of a video before normalising it and saving the results to a plain text file.

\lstinputlisting{code-listings/histogram/generate_and_store_average_hsv_histogram.py}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Matching 2D Histograms}
\label{sec:code-match_2D_histograms}

describe

\lstinputlisting{code-listings/histogram/match_2D_histograms.py}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Matching 3D Histograms}
\label{sec:code-match_3D_histograms}

describe

\lstinputlisting{code-listings/histogram/match_3D_histograms.py}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Shot Boundary Algorithm}
\label{sec:code-shot_boundary_detection}

Compares consecutive frames' RGB histograms using the Intersection metric with a global threshold approach. If the metric is smaller than the specified threshold, then a shot boundary has been detected.

\lstinputlisting{code-listings/histogram/shot_boundary_detection.py}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Frames Pre-Selection Function}
\label{sec:code-get_frames_to_process}

Returns the IDs of the frames to calculate a histogram for (1 frame per second).

\lstinputlisting{code-listings/histogram/get_frames_to_process.py}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% VIDEO OPERATIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\section{Video Operations Module}

The \textit{video\_operations.py} module contains the code used to perform operations on the query video. It takes care of the pre-processing steps, including video stabilisation and manual ROI selection. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{VideoStabiliser Class}
\label{sec:code-VideoStabiliser}

Class used to stabilise the recorded video for more optimal matching.

\lstinputlisting{code-listings/video_operations/VideoStabiliser.py}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{ClickAndDrop Class for Manual ROI Selection}
\label{sec:code-ClickAndDrop}

Class for selecting a region of interest on a frame by click and dropping the mouse over the desired area, and cropping that frame to include the pixels inside the ROI only.

\lstinputlisting{code-listings/video_operations/ClickAndDrop.py}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% HELPERS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\section{Helpers Module}

describe module

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Generate Single Histogram}
% \label{sec:code-generate-single-histogram}

% \lstinputlisting[caption=Function generating histograms for the pre-selected frames and adding them to lists before averaging them to create a video's compact signature.]{code-listings/generate_single_histogram.py}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%