This document describes the 13 issues that need to be considered carefully before students or staff  involve other people (“participants”) for the collection of information as part of their project or research.

\begin{enumerate}
    \item \textbf{Have you prepared a briefing script for volunteers}?\\
    All participants will be introduced with a briefing script explaining what the project consists in, what their role in the experiment is, and how their data will be used.
    \item \textbf{Will the participants be using any non-standard hardware?}\\
    No. Participants can conduct the experiment from their personal computers or mobile devices.
    \item \textbf{Is there any intentional deception of the participants?}\\
    No deception will occur during this experiment, all the details of the experiment will be provided in the debriefing script.
    \item \textbf{How will participants voluntarily give consent?}\\
    The participants will give consent when they submit their Google Form survey, which is specified in the briefing script.
    \item \textbf{Will the participants be exposed to any risks greater than those encountered in their normal work life?}\\
    Participants will take part in the experiment from their normal environments as they will be receive a link to the online survey in their personal inbox, which they can use to access the survey online from their personal computers and mobile devices.
    \item \textbf{Are you offering any incentive to the participants?}\\
    No incentive will be offered to participants.
    \item \textbf{Are any of your participants under the age of 16?}\\
    All participants are above the age of 18.
    \item \textbf{Do any of your participants have an impairment that will limit their understanding or communication?}\\
    None of the participants have any known impairment which may affect the experiment's results.
    \item \textbf{Are you in a position of authority or influence over any of your 	participants?}\\
    The participants will complete the survey in their own free time using their own hardware with no presence of authority present during the experiment.
    \item \textbf{Will the participants be informed that they could withdraw at any time?}\\
    All the participants will be informed that they can withdraw from the experiment at any time in the briefing script.
    \item \textbf{Will the participants be informed of your contact details?}
    My contacts details and my supervisor's details will be shared with all participants.
    \item \textbf{Will participants be de-briefed?}\\
    All participants will be debriefed through the introductory briefing script.
    \item \textbf{Will the data collected from the participants be stored in an anonymous form?}\\
    The data collected from the online survey will be downloaded and stored locally in a CSV file anonymously, and will be used anonymously in the final report, as informed in the briefing script.
\end{enumerate}